The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

>>>>

When cultural factors are looked at, they are considered as a given feature that can hardly be traced. By having a closer look at education systems, we intend to look at the processes through which some of these cultural patterns are enhanced and passed from one generation to the next. Aside of parental education, schools are indeed the very place where children are taught how to fit in the society. This research is an attempt at looking at one trait in particular
